---
title: \bf\textsc{\large QR(week1)} 
subtitle: \textsc{\today}
documentclass: article
fontsize: 10pt 
geometry: margin=0.45in 
output: pdf_document
header-includes:
  - \usepackage{palatino}
  - \usepackage[singlespacing]{setspace}
  - \usepackage{hyperref}
  - \usepackage{amsthm}
  - \usepackage{amsmath}
  - \usepackage{enumitem}
  - \usepackage{subfigure}
  - \usepackage{float}
  - \newtheoremstyle{sol}{3pt}{2pt}{}{}{\bfseries}{.}{.5em}{}
  - \theoremstyle{sol}
  - \newtheorem*{sol}{Suggested Solution}
  - \newcommand{\benum}{\begin{enumerate}[label=(\alph*)]}
  - \newcommand{\eenum}{\end{enumerate}}
  - \newcommand{\bitem}{\begin{itemize}}
  - \newcommand{\eitem}{\end{itemize}}
---

```{r setup, echo=FALSE}
library(knitr)
knitr::opts_chunk$set(echo = TRUE, prompt=FALSE, message=FALSE,comment=NA,warning=FALSE,collapse=TRUE , fig.align="center")
```

```{r library, echo=FALSE}
if(!require(ggplot2)){
    install.packages("ggplot2")
    library(ggplot2)
}
if(!require(quantreg)){
    install.packages("quantreg")
    library(quantreg)
}
```

\section{Part I: Simulation}
\subsection{1. Generate Dataset}

Following the data generating process:

\begin{align*}
&y_i = (1+\beta x_i)(u_i+3)\\
&u|x \sim \chi^2_3\\
&x \sim \chi^2_6
\end{align*}

Here, I choose $\beta = 1$ and set seed(123) to fix the data.

```{r}
# test with a seed
set.seed(123)
u = data.frame(u=rchisq(1:300, df=3))
x = data.frame(x=rchisq(1:300, df=6))
beta = 1
y = data.frame(y = (1+beta*x)*(u+3))
colnames(y) <- c('y')
df <- cbind(x,y)
```

\subsection{2. Plot}

Mimicking the code for plotting in the `rq` tutorial, the graph below plots $Q_{y|x}(\tau)$ for $\tau \in (.05,.1,.25,.75,.90,.95)$
the graph below proved heteroskedasticity. ($\beta = 1, N = 300$)

```{r}
plot(df, cex=.6, col="blue")
taus <- c(.05,.1,.25,.75,.90,.95)
for( i in 1:length(taus)){
  abline(rq(y~x,tau=taus[i],data=df),col="gray")}
abline(rq(y~x,tau=.5,data=df),col="blue")
abline(lm(y~x,data=df),lty=2,col="red")#the dreaded ols line
```

\subsection{3. Quantile Model fit}

Fitting the quantile model:

$$
Q_{y|x}(\tau) = \beta_{0,\tau} + \beta_{1,\tau} x
$$

with $\tau = 0.25$

```{r}
fit25 <- rq(y ~ x, tau = .25,data=df)
summary(fit25,se="ker")
```


\subsection{4. Bias, Variance, MSE}


Epanechnikov kernel is chosen to compute the standard error.

\subsubsection{different $\beta$s}

```{r}
maxit = 1000 # number of iteration
betas = seq.int(0, 5) # sequence of betas
nb = length(betas) # number of betas

# create df to store the results
resultdf <- setNames(data.frame(matrix(ncol = 4, nrow = nb)), c("beta", "bias", "var", "mse")) 
# initialize the df to store se for each beta's 1000 iteration results
se <- setNames(data.frame(matrix(ncol = nb, nrow = maxit)), betas)
bhat <- setNames(data.frame(matrix(ncol = nb, nrow = maxit)), betas)

for (i in 1:nb){
  beta = betas[i]
  for (j in 1:maxit){
    u = data.frame(u=rchisq(1:300, df=3))
    x = data.frame(x=rchisq(1:300, df=6))
    y = data.frame(y = (1+beta*x)*(u+3))
    colnames(y) <- c('y')
    df <- cbind(x,y)
    fit25 <- rq(y ~ x, tau = .25,data=df)
    se[j,i]  <- summary(fit25,se="ker")$coefficients[2,2]
    bhat[j,i]<- summary(fit25,se="ker")$coefficients[2,1]
  }
  resultdf$beta[i] = beta
  bias= sum(se[,i])/1000 - beta
  resultdf$bias[i] = bias
  var = var(se[,i])
  resultdf$var[i] =var
  resultdf$mse[i] = bias^2+var
}
```

```{r}
# For different beta in data generating process
# Bias, Variance, MSE
head(resultdf)
# Computed standard error (ker)
head(se)
# Predicted \beta_{1,\tau}
head(bhat)
```

\subsubsection{different taus}

```{r}
maxit = 1000 # number of iteration
taus <- seq.int(0.1, 1, 0.1) # sequence of taus
nb = length(taus) # number of taus
beta = 0 # data generating process

resultdf <- setNames(data.frame(matrix(ncol = 4, nrow = nb)), c("tau", "bias", "var", "mse"))
# initialize the df to store se for each tau's 1000 iteration results
bhat <- setNames(data.frame(matrix(ncol = nb, nrow = maxit)), taus)
se <- setNames(data.frame(matrix(ncol = nb, nrow = maxit)), taus)

for (i in 1:nb){
  mytau = taus[i]
  for (j in 1:maxit){
    u = data.frame(u=rchisq(1:300, df=3))
    x = data.frame(x=rchisq(1:300, df=6))
    y = data.frame(y = (1+beta*x)*(u+3)) # beta is set to be 0 in this case
    colnames(y) <- c('y')
    df <- cbind(x,y)
    fit <- rq(y ~ x, tau = mytau,data=df)
    se[j,i]  <- summary(fit,se="ker")$coefficients[2,2]
    bhat[j,i]<- summary(fit,se="ker")$coefficients[2,1]
  }
  resultdf$tau[i] = mytau
  bias= sum(se[,i])/1000 - beta
  resultdf$bias[i] = bias
  var = var(se[,i])
  resultdf$var[i] =var
  resultdf$mse[i] = bias^2+var
}
```

```{r}
# For different taus
# Bias, Variance, MSE
head(resultdf)
# Computed standard error (ker)
head(se)
# Predicted \beta_{1,\tau}
head(bhat)
```

\subsection{Type II Error}

\subsubsection{different taus}

```{r}
for (i in 1:nb){
  print(sum(abs((bhat[,i]-beta)/se[,i])>1.96)/maxit)
}
```



To be continued...
QTM 385 - Homework 5




